---
title: "Zooplankton and Rotifer QA Report"
output: html_document
params:
  raw_files: NULL
  unknown_protocol: NULL
  zoop_data: NULL
  rot_data: NULL
  zoop_qa_summary: NULL
  rot_qa_summary: NULL
  zoop_sample_summary: NULL
  rot_sample_summary: NULL
  zoop_missing_required: NULL
  zoop_negative_counts: NULL
  zoop_nonpositive_split_factor: NULL
  zoop_unexpected_sex_values: NULL
  zoop_duplicate_organism_rows: NULL
  zoop_station_standardization: NULL
  zoop_qa_link_issues: NULL
  zoop_split_factor_consistency: NULL
  zoop_multiple_analyst_dates: NULL
  zoop_missing_analyst_date: NULL
  zoop_missing_split_on_counted_rows: NULL
  rot_missing_required: NULL
  rot_negative_counts: NULL
  rot_nonpositive_split_factor: NULL
  rot_duplicate_organism_rows: NULL
  rot_station_standardization: NULL
  rot_qa_link_issues: NULL
  rot_split_factor_consistency: NULL
  rot_multiple_analyst_dates: NULL
  rot_missing_analyst_date: NULL
  rot_missing_split_on_counted_rows: NULL
  rot_missing_rotvol: NULL
  rot_missing_subml: NULL
  rot_nonpositive_rotvol: NULL
  rot_nonpositive_subml: NULL
  rot_unexpected_splits: NULL
  rot_width_without_length: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(targets)
library(dplyr)
library(tibble)

raw_files <- params$raw_files
unknown_protocol <- params$unknown_protocol

zoop_data <- params$zoop_data
rot_data <- params$rot_data

zoop_qa_summary <- params$zoop_qa_summary
rot_qa_summary <- params$rot_qa_summary

zoop_sample_summary <- params$zoop_sample_summary
rot_sample_summary <- params$rot_sample_summary

zoop_missing_required <- params$zoop_missing_required
zoop_negative_counts <- params$zoop_negative_counts
zoop_nonpositive_split_factor <- params$zoop_nonpositive_split_factor
zoop_unexpected_sex_values <- params$zoop_unexpected_sex_values
zoop_duplicate_organism_rows <- params$zoop_duplicate_organism_rows
zoop_station_standardization <- params$zoop_station_standardization
zoop_qa_link_issues <- params$zoop_qa_link_issues
zoop_split_factor_consistency <- params$zoop_split_factor_consistency
zoop_multiple_analyst_dates <- params$zoop_multiple_analyst_dates
zoop_missing_analyst_date <- params$zoop_missing_analyst_date
zoop_missing_split_on_counted_rows <- params$zoop_missing_split_on_counted_rows

rot_missing_required <- params$rot_missing_required
rot_negative_counts <- params$rot_negative_counts
rot_nonpositive_split_factor <- params$rot_nonpositive_split_factor
rot_duplicate_organism_rows <- params$rot_duplicate_organism_rows
rot_station_standardization <- params$rot_station_standardization
rot_qa_link_issues <- params$rot_qa_link_issues
rot_split_factor_consistency <- params$rot_split_factor_consistency
rot_multiple_analyst_dates <- params$rot_multiple_analyst_dates
rot_missing_analyst_date <- params$rot_missing_analyst_date
rot_missing_split_on_counted_rows <- params$rot_missing_split_on_counted_rows
rot_missing_rotvol <- params$rot_missing_rotvol
rot_missing_subml <- params$rot_missing_subml
rot_nonpositive_rotvol <- params$rot_nonpositive_rotvol
rot_nonpositive_subml <- params$rot_nonpositive_subml
rot_unexpected_splits <- params$rot_unexpected_splits
rot_width_without_length <- params$rot_width_without_length
```

## Overview

```{r}
data.frame(
  metric = c(
    "Number of raw files",
    "Unknown protocol files",
    "Zoop rows",
    "Rot rows",
    "Zoop unique samples",
    "Rot unique samples"
  ),
  value = c(
    length(raw_files),
    nrow(unknown_protocol),
    nrow(zoop_data),
    nrow(rot_data),
    dplyr::n_distinct(zoop_data$sample_num),
    dplyr::n_distinct(rot_data$sample_num)
  )
) |>
  knitr::kable()
```

## Unknown protocol files

```{r}
if (nrow(unknown_protocol) == 0) {
  knitr::kable(data.frame(message = "No unknown protocol files detected."))
} else {
  knitr::kable(unknown_protocol)
}
```

# Zooplankton QA
## Zoop overview

```{r}
data.frame(
  n_rows = nrow(zoop_data),
  n_samples = dplyr::n_distinct(zoop_data$sample_num),
  n_source_files = dplyr::n_distinct(zoop_data$source_file),
  n_taxa = dplyr::n_distinct(zoop_data$species_name)
) |>
  knitr::kable()
```

## Zoop QA summary

```{r}
zoop_qa_summary |>
  knitr::kable()
```

## Zoop Sample summary

```{r}
zoop_sample_summary |>
  dplyr::arrange(source_file, sample_num, split) |>
  knitr::kable()
```

## Zoop Missing required values

```{r}
zoop_missing_required |>
  head(50) |>
  knitr::kable()
```

## Zoop Negative counts

```{r}
zoop_negative_counts |>
  head(50) |>
  knitr::kable()
```

## Zoop nonpositive split factor

```{r}
zoop_nonpositive_split_factor |>
  head(50) |>
  knitr::kable()
```

## Zoop unexpected sex values

```{r}
zoop_unexpected_sex_values |>
  head(50) |>
  knitr::kable()
```

## Zoop duplicate organism rows

```{r}
zoop_duplicate_organism_rows |>
  head(50) |>
  knitr::kable()
```

## Zoop Station standardization

```{r}
zoop_station_standardization |>
  head(50) |>
  knitr::kable()
```

## Zoop QA link issues

```{r}
zoop_qa_link_issues |>
  head(50) |>
  knitr::kable()
```

## Zoop split factor consistency

```{r}
zoop_split_factor_consistency |>
  head(50) |>
  knitr::kable()
```

## Zoop multiple analyst dates

```{r}
zoop_multiple_analyst_dates |>
  head(50) |>
  knitr::kable()
```

## Zoop missing analyst dates

```{r}
zoop_missing_analyst_date |>
  head(50) |>
  knitr::kable()
```

## Zoop missing split on counted rows

```{r}
zoop_missing_split_on_counted_rows |>
  head(50) |>
  knitr::kable()
```

# Rotifer QA
## Rot overview

```{r}
data.frame(
  n_rows = nrow(rot_data),
  n_samples = dplyr::n_distinct(rot_data$sample_num),
  n_source_files = dplyr::n_distinct(rot_data$source_file),
  n_taxa = dplyr::n_distinct(rot_data$species_name)
) |>
  knitr::kable()
```

## Zoop QA summary

```{r}
rot_sample_summary |>
  dplyr::arrange(source_file, sample_num, split) |>
  knitr::kable()
```

## Zoop Sample summary

```{r}
zoop_sample_summary |>
  dplyr::arrange(source_file, sample_num, split) |>
  knitr::kable()
```

## Zoop Missing required values

```{r}
rot_missing_required |>
  head(50) |>
  knitr::kable()
```

## Zoop Negative counts

```{r}
rot_negative_counts |>
  head(50) |>
  knitr::kable()
```

## Zoop nonpositive split factor

```{r}
rot_nonpositive_split_factor |>
  head(50) |>
  knitr::kable()
```

## Zoop duplicate organism rows

```{r}
rot_duplicate_organism_rows |>
  head(50) |>
  knitr::kable()
```

## Zoop Station standardization

```{r}
rot_station_standardization |>
  head(50) |>
  knitr::kable()
```

## Zoop QA link issues

```{r}
rot_qa_link_issues |>
  head(50) |>
  knitr::kable()
```

## Zoop split factor consistency

```{r}
rot_split_factor_consistency |>
  head(50) |>
  knitr::kable()
```

## Zoop multiple analyst dates

```{r}
rot_multiple_analyst_dates |>
  head(50) |>
  knitr::kable()
```

## Zoop missing analyst dates

```{r}
rot_missing_analyst_date |>
  head(50) |>
  knitr::kable()
```

## Zoop missing split on counted rows

```{r}
rot_missing_split_on_counted_rows |>
  head(50) |>
  knitr::kable()
```

## Rot missing ROTVOL

```{r}
rot_missing_rotvol |>
  head(50) |>
  knitr::kable()
```

## Rot missing split-specific aliquot volume

```{r}
rot_missing_subml |>
  head(50) |>
  knitr::kable()
```

## Rot nonpositive ROTVOL

```{r}
rot_nonpositive_rotvol |>
  head(50) |>
  knitr::kable()
```

## Rot nonpositive split-specific aliquot volume

```{r}
rot_nonpositive_subml |>
  head(50) |>
  knitr::kable()
```

## Rot unexpected splits

```{r}
rot_unexpected_splits |>
  head(50) |>
  knitr::kable()
```

## Rot width recorded without length

```{r}
rot_unexpected_splits |>
  head(50) |>
  knitr::kable()
```

