---
title: "Zooplankton and Rotifer QA Report"
output: html_document
params:
  raw_files: NULL
  unknown_protocol: NULL
  zoop_data: NULL
  rot_data: NULL
  zoop_qa_summary: NULL
  rot_qa_summary: NULL
  zoop_sample_summary: NULL
  rot_sample_summary: NULL
  zoop_missing_required: NULL
  zoop_negative_counts: NULL
  zoop_nonpositive_split_factor: NULL
  zoop_unexpected_sex_values: NULL
  zoop_duplicate_organism_rows: NULL
  zoop_station_standardization: NULL
  zoop_qa_link_issues: NULL
  zoop_split_factor_consistency: NULL
  zoop_multiple_analyst_dates: NULL
  zoop_missing_analyst_date: NULL
  zoop_missing_split_on_counted_rows: NULL
  zoop_unexpected_power_used: NULL
  zoop_d_split_allowed_taxa: NULL
  rot_missing_required: NULL
  rot_negative_counts: NULL
  rot_nonpositive_split_factor: NULL
  rot_duplicate_organism_rows: NULL
  rot_station_standardization: NULL
  rot_qa_link_issues: NULL
  rot_split_factor_consistency: NULL
  rot_multiple_analyst_dates: NULL
  rot_missing_analyst_date: NULL
  rot_missing_split_on_counted_rows: NULL
  rot_missing_rotvol: NULL
  rot_missing_subml: NULL
  rot_nonpositive_rotvol: NULL
  rot_nonpositive_subml: NULL
  rot_unexpected_splits: NULL
  rot_required_length_and_width: NULL
  rot_collotheca_width_only: NULL
  rot_unexpected_width_without_length: NULL
  rot_unexpected_power_used: NULL
  sample_not_in_master: NULL
  master_sample_missing_in_data: NULL
  station_mismatch_vs_master: NULL
  depth_mismatch_vs_master: NULL
  species_code_not_in_key: NULL
  species_metadata_mismatch: NULL
  d20_sample_id_suffix: NULL
  d100_sample_id_suffix: NULL
  rot_not_allowed_in_d100: NULL
  d20_missing_protocol_pair: NULL
  zoop_flagged_data: NULL
  rot_flagged_data: NULL
  
---

# This file creates the HTML QA report.
#
# The report does not import raw data directly.
# Instead, _targets.R passes cleaned data, QA tables, and summaries into it.
#
# The report provides:
#   - project overview
#   - Zoop QA summary
#   - Rot QA summary
#   - master-list validation results
#   - examples of flagged records for review
#
# The output is written to:
#   outputs/qa_report.html

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

raw_files <- params$raw_files
unknown_protocol <- params$unknown_protocol

zoop_data <- params$zoop_data
rot_data <- params$rot_data

zoop_qa_summary <- params$zoop_qa_summary
rot_qa_summary <- params$rot_qa_summary

zoop_sample_summary <- params$zoop_sample_summary
rot_sample_summary <- params$rot_sample_summary

zoop_missing_required <- params$zoop_missing_required
zoop_negative_counts <- params$zoop_negative_counts
zoop_nonpositive_split_factor <- params$zoop_nonpositive_split_factor
zoop_unexpected_sex_values <- params$zoop_unexpected_sex_values
zoop_duplicate_organism_rows <- params$zoop_duplicate_organism_rows
zoop_station_standardization <- params$zoop_station_standardization
zoop_qa_link_issues <- params$zoop_qa_link_issues
zoop_split_factor_consistency <- params$zoop_split_factor_consistency
zoop_multiple_analyst_dates <- params$zoop_multiple_analyst_dates
zoop_missing_analyst_date <- params$zoop_missing_analyst_date
zoop_missing_split_on_counted_rows <- params$zoop_missing_split_on_counted_rows
zoop_unexpected_power_used <- params$zoop_unexpected_power_used
zoop_d_split_allowed_taxa <- params$zoop_d_split_allowed_taxa
zoop_flagged_data <- params$zoop_flagged_data

rot_flagged_data <- params$rot_flagged_data
rot_missing_required <- params$rot_missing_required
rot_negative_counts <- params$rot_negative_counts
rot_nonpositive_split_factor <- params$rot_nonpositive_split_factor
rot_duplicate_organism_rows <- params$rot_duplicate_organism_rows
rot_station_standardization <- params$rot_station_standardization
rot_qa_link_issues <- params$rot_qa_link_issues
rot_split_factor_consistency <- params$rot_split_factor_consistency
rot_multiple_analyst_dates <- params$rot_multiple_analyst_dates
rot_missing_analyst_date <- params$rot_missing_analyst_date
rot_missing_split_on_counted_rows <- params$rot_missing_split_on_counted_rows
rot_missing_rotvol <- params$rot_missing_rotvol
rot_missing_subml <- params$rot_missing_subml
rot_nonpositive_rotvol <- params$rot_nonpositive_rotvol
rot_nonpositive_subml <- params$rot_nonpositive_subml
rot_unexpected_splits <- params$rot_unexpected_splits
rot_required_length_and_width <- params$rot_required_length_and_width
rot_collotheca_width_only <- params$rot_collotheca_width_only
rot_unexpected_width_without_length <- params$rot_unexpected_width_without_length
rot_unexpected_power_used <- params$rot_unexpected_power_used

sample_not_in_master <- params$sample_not_in_master
master_sample_missing_in_data <- params$master_sample_missing_in_data
station_mismatch_vs_master <- params$station_mismatch_vs_master
depth_mismatch_vs_master <- params$depth_mismatch_vs_master
species_code_not_in_key <- params$species_code_not_in_key
species_metadata_mismatch <- params$species_metadata_mismatch
d20_sample_id_suffix <- params$d20_sample_id_suffix
d100_sample_id_suffix <- params$d100_sample_id_suffix
rot_not_allowed_in_d100 <- params$rot_not_allowed_in_d100
d20_missing_protocol_pair <- params$d20_missing_protocol_pair
```

## Overview

```{r}
data.frame(
  metric = c(
    "Number of raw files",
    "Unknown protocol files",
    "Zoop rows",
    "Rot rows",
    "Zoop unique samples",
    "Rot unique samples"
  ),
  value = c(
    length(raw_files),
    nrow(unknown_protocol),
    nrow(zoop_data),
    nrow(rot_data),
    dplyr::n_distinct(zoop_data$sample_num),
    dplyr::n_distinct(rot_data$sample_num)
  )
) |>
  knitr::kable()
```

## Unknown protocol files

```{r}
if (nrow(unknown_protocol) == 0) {
  knitr::kable(data.frame(message = "No unknown protocol files detected."))
} else {
  knitr::kable(unknown_protocol)
}
```

# Master List Validation
## Samples not in master list

```{r}
sample_not_in_master |>
  head(50) |>
  knitr::kable()
```

## Master samples missing in compiled data

```{r}
master_sample_missing_in_data |>
  head(50) |>
  knitr::kable()
```

## Station mismatches vs master list

```{r}
station_mismatch_vs_master |>
  head(50) |>
  knitr::kable()
```

## Depth mismatches vs master list

```{r}
depth_mismatch_vs_master |>
  head(50) |>
  knitr::kable()
```

## D20 sample IDs not ending in 4

```{r}
d20_sample_id_suffix |>
  head(50) |>
  knitr::kable()
```

## D100 Zoop sample IDs not ending in 3

```{r}
d100_sample_id_suffix |>
  head(50) |>
  knitr::kable()
```

## Rot samples incorrectly present for D100

```{r}
rot_not_allowed_in_d100 |>
  head(50) |>
  knitr::kable()
```

## D20 missing required Zoop/Rot protocol pair

```{r}
rot_not_allowed_in_d100 |>
  head(50) |>
  knitr::kable()
```

# Species Key Validation
## Species codes not found in GLNPO species key

```{r}
species_code_not_in_key |>
  head(50) |>
  knitr::kable()
```

# Species metadata mismatches

```{r}
species_metadata_mismatch |>
  head(50) |>
  knitr::kable()
```


# Zooplankton QA
## Zoop overview

```{r}
data.frame(
  n_rows = nrow(zoop_data),
  n_samples = dplyr::n_distinct(zoop_data$sample_num),
  n_source_files = dplyr::n_distinct(zoop_data$source_file),
  n_taxa = dplyr::n_distinct(zoop_data$species_name)
) |>
  knitr::kable()
```

## Zoop QA summary

```{r}
zoop_qa_summary |>
  knitr::kable()
```

## Zoop Sample summary

```{r}
zoop_sample_summary |>
  dplyr::arrange(source_file, sample_num, split) |>
  knitr::kable()
```

## Zoop Missing required values

```{r}
zoop_missing_required |>
  head(50) |>
  knitr::kable()
```

## Zoop Negative counts

```{r}
zoop_negative_counts |>
  head(50) |>
  knitr::kable()
```

## Zoop nonpositive split factor

```{r}
zoop_nonpositive_split_factor |>
  head(50) |>
  knitr::kable()
```

## Zoop unexpected sex values

```{r}
zoop_unexpected_sex_values |>
  head(50) |>
  knitr::kable()
```

## Zoop duplicate organism rows

```{r}
zoop_duplicate_organism_rows |>
  head(50) |>
  knitr::kable()
```

## Zoop Station standardization

```{r}
zoop_station_standardization |>
  head(50) |>
  knitr::kable()
```

## Zoop QA link issues

```{r}
zoop_qa_link_issues |>
  head(50) |>
  knitr::kable()
```

## Zoop split factor consistency

```{r}
zoop_split_factor_consistency |>
  head(50) |>
  knitr::kable()
```

## Zoop multiple analyst dates

```{r}
zoop_multiple_analyst_dates |>
  head(50) |>
  knitr::kable()
```

## Zoop missing analyst dates

```{r}
zoop_missing_analyst_date |>
  head(50) |>
  knitr::kable()
```

## Zoop missing split on counted rows

```{r}
zoop_missing_split_on_counted_rows |>
  head(50) |>
  knitr::kable()
```

## Zoop unexpected power used

```{r}
zoop_unexpected_power_used |>
  head(50) |>
  knitr::kable()
```

## Zoop split taxa outside allowed adult list

```{r}
zoop_d_split_allowed_taxa |>
  head(50) |>
  knitr::kable()
```

# Rotifer QA
## Rot overview

```{r}
data.frame(
  n_rows = nrow(rot_data),
  n_samples = dplyr::n_distinct(rot_data$sample_num),
  n_source_files = dplyr::n_distinct(rot_data$source_file),
  n_taxa = dplyr::n_distinct(rot_data$species_name)
) |>
  knitr::kable()
```

## Rot QA summary

```{r}
rot_qa_summary |>
  knitr::kable()
```

## Rot Sample summary

```{r}
rot_sample_summary |>
  dplyr::arrange(source_file, sample_num, split) |>
  knitr::kable()
```

## Rot Missing required values

```{r}
rot_missing_required |>
  head(50) |>
  knitr::kable()
```

## Rot negative counts

```{r}
rot_negative_counts |>
  head(50) |>
  knitr::kable()
```

## Rot nonpositive split factor

```{r}
rot_nonpositive_split_factor |>
  head(50) |>
  knitr::kable()
```

## Rot duplicate organism rows

```{r}
rot_duplicate_organism_rows |>
  head(50) |>
  knitr::kable()
```

## Rot Station standardization

```{r}
rot_station_standardization |>
  head(50) |>
  knitr::kable()
```

## Rot QA link issues

```{r}
rot_qa_link_issues |>
  head(50) |>
  knitr::kable()
```

## Rot split factor consistency

```{r}
rot_split_factor_consistency |>
  head(50) |>
  knitr::kable()
```

## Rot multiple analyst dates

```{r}
rot_multiple_analyst_dates |>
  head(50) |>
  knitr::kable()
```

## Rot missing analyst dates

```{r}
rot_missing_analyst_date |>
  head(50) |>
  knitr::kable()
```

## Rot missing split on counted rows

```{r}
rot_missing_split_on_counted_rows |>
  head(50) |>
  knitr::kable()
```

## Rot missing ROTVOL

```{r}
rot_missing_rotvol |>
  head(50) |>
  knitr::kable()
```

## Rot missing split-specific aliquot volume

```{r}
rot_missing_subml |>
  head(50) |>
  knitr::kable()
```

## Rot nonpositive ROTVOL

```{r}
rot_nonpositive_rotvol |>
  head(50) |>
  knitr::kable()
```

## Rot nonpositive split-specific aliquot volume

```{r}
rot_nonpositive_subml |>
  head(50) |>
  knitr::kable()
```

## Rot unexpected splits

```{r}
rot_unexpected_splits |>
  head(50) |>
  knitr::kable()
```

## Rot unexpected width without length

```{r}
rot_unexpected_width_without_length |>
  head(50) |>
  knitr::kable()
```

## Rot unexpected power used

```{r}
rot_unexpected_power_used |>
  head(50) |>
  knitr::kable()
```

## Rot taxa requiring both length and width

```{r}
rot_required_length_and_width |>
  head(50) |>
  knitr::kable()
```

## Rot Collotheca rows missing required width

```{r}
rot_collotheca_width_only |>
  head(50) |>
  knitr::kable()
```

## Flagged row overview

```{r}
data.frame(
  dataset = c("Zoop", "Rot"),
  flagged_rows = c(
    sum(zoop_flagged_data$any_flag, na.rm = TRUE),
    sum(rot_flagged_data$any_flag, na.rm = TRUE)
  )
) |>
  knitr::kable()
```
